Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2015-08-03 phaseDelay.tex
Updates from ShareLaTeX

In this paper, we have examined contemporary project data for traces of
the widely-believed delayed issue effect.
We found that, in the literature, the evidence for this effect was very spare--
in fact, we found
just as many articles supporting this  exponential effect~\cite{Boehm76,Boehm81,teck,Fagan76,Stephenson76}
than otherwise~\cite{Clutterbuck09,Clutterbuck09,Boehm80} and one paper that
offered evidence consistent with {\em both}
the the delayed issue effect and its opposite~\cite{shull02}.

@@

\subsection{Future Work}
There is another ``phase delay'' effect, not discussed above. Even if software is readily updatable, there   may be a ``user phase delay''   amongst   humans using that software.

>>>>

In this paper, we have examined contemporary project data for traces of
the widely-believed delayed issue effect.
We found that, in the literature, the evidence for this effect was very spare--
in fact, we found
just as many articles supporting this  exponential effect~\cite{Boehm76,Boehm81,steck04,Fagan76,Stephenson76}
than otherwise~\cite{Clutterbuck09,Clutterbuck09,Boehm80} and one paper that
offered evidence consistent with {\em both}
the the delayed issue effect and its opposite~\cite{Shull02}.

@@

\section{Future Work}
There is another ``phase delay'' effect, not discussed above. Even if software is readily updatable, there   may be a ``user phase delay''   amongst   humans using that software.
